Spin canonical divisors of log stacky curves

### 2015-06-30 stacky_write_up/spin_cring.tex
edited examples a bit

\begin{example}
\label{eg:base-1-0}
In the case $\halfcan' = 0,$ it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
\end{example}

\begin{example}
\label{ex:base-377}
Here we demonstrate, in detail, that case (b) with ($\sigma =
(0; 3, 7, 7; 0), \halfcan' \sim -\infty + \frac{1}{3} P_1 +
\frac{3}{7} P_2 + \frac{3}{7} P_3, J = \{3, 4\},$) with distinct points $P_i \neq \infty$,
satisfies the conditions of Lemma ~\ref{lem:g-0-admissible-cases}.
We exhibit a (minimal) presentation for $R'$.

@@

By the Generalized Max Noether Theorem for genus 0 curves, (see Voight
and Zureick-Brown \cite[Lemma 3.1.1]{vzb:stacky}),
\[
	H^0 (\sx', \lfloor 21 \cdot \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
	(d - 21) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
	d \halfcan' \rfloor)
\]

\noindent
is surjective whenever $\deg (\lfloor (d - 21) K_{\sx'} \rfloor)
\geq 0$. Since $\sigma$ has saturation $s = 5$, as noted in
Table ~\ref{table:g-0-sat}, then this map is surjective
when $d \geq 21 + s = 26$ (i.e. $R'$ is generated up to degree 25).

@@

\begin{figure}[H]
\label{fig:377}
\includegraphics{pics/spin-377-pic-pics.pdf} \\
\caption{Generators in the $(\deg z, -ord_{P_i}(z))$ lattice}
\end{figure}

@@

\begin{example}
\label{eg:base-1-33}
Let $\sx'$ be a stacky curve so that $\halfcan' = P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$. In this example, we show
$$R_{\halfcan'} \cong k[u, x_3, y_3, y_4]/(x_3 y_3- \alpha uy_4, y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$
and that $(\sx', \halfcan',\{1,2\})$ is admissible.

@@

\begin{example}
\label{eg:exception-1-5}
Let $L' = P - Q + \frac{2}{5}P_1$ be a spin canonical divisor on a stacky curve $\sx$. Let $u \in (P_L)_1$ be any nonzero element. We obtain $\di u|_{P_1} = 0,$ since $2P -2Q \sim 0$ and by Riemann--Roch, $\dim_k (P_L)_1 = 1.$ Let $y_3 \in (R_L)_3$ be any nonzero element. We obtain $\di y_3|_{P_1} = - P_1,$ by Riemann Roch, since if $y_3$ did not have a pole at $R$, we would obtain $y_3 \in H^0(\sx,3P-3Q) \cong H^0(\sx, P - Q) \cong 0$ as $P \neq Q$. Finally, let $y_5 \in (R_L)_5$ be an element with $y_5|_{P_1} = -P_1$. Then, we claim there is some $\alpha \in k$ so that
$R_L \cong k[u, y_3, y_5]/(y_3^4 - \alpha uy_5^2).$

@@

Note that $(\sx', \halfcan', \{1\})$ is admissible, as can be checked in a fashion analogous to the verification in Example ~\ref{eg:base-1-33}.

Finally, note that this particular case is also exceptional, because there is a relation in degree $12 > 2 \cdot 5$, but once $e' = 5$ is incremented to $e = e'+2 = 7,$ using Lemma ~\ref{lem:raise-stacky-order}, this relation in degree 12 also determines a relation in the canonical ring for $L = P - Q + \frac{3}{7}$, and so the case $L' = P - Q + \frac{3}{7}P_1$ is not exceptional because $12 < 2 \cdot 7$.
\end{example}

>>>>

\begin{example}
\label{eg:base-1-0}
Let $(\sx',0,\halfcan')$ be a log stacky curve of genus $g = 1$. In the case $\halfcan' = 0,$ it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
\end{example}

\begin{example}
\label{ex:base-377}
Let $(\sx,0,\halfcan')$ be a log spin curve with signature $\sigma =
(0; 3, 7, 7; 0)$ and $\halfcan' \sim -\infty + \frac{1}{3} P_1 +
\frac{3}{7} P_2 + \frac{3}{7} P_3,$ where $P_1,P_2,$ and $P_3$ are distinct points. In this example, we will exhibit a minimal presentation for $R' = R(\sx,0,\halfcan')$ and show the triple $(\sigma, \halfcan' + \frac{3}{7} P_3, J = \{2, 3\},$) is admissible.

@@

By the Generalized Max Noether Theorem for genus 0 curves, (see Voight
and Zureick-Brown \cite[Lemma 3.1.1]{vzb:stacky}),
\begin{align}
\label{eqn:noether-377}
	H^0 (\sx', \lfloor 21 \cdot \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
	(d - 21) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
	d \halfcan' \rfloor)
\end{align}

\noindent
is surjective whenever $\deg (\lfloor (d - 21) K_{\sx'} \rfloor)
\geq 0$. It is fairly easy to see using Riemann--Roch that $\sat(\Eff(\sigma)) = 5.$
Then the map in ~\eqref{eqn:noether-377} is surjective
when $d \geq 21 + s = 26$ (i.e. $R'$ is generated up to degree 25).

@@

\begin{figure}[H]
\includegraphics{pics/spin-377-pic-pics.pdf} \\
\caption{Generators in the $(\deg z, -ord_{P_i}(z))$ lattice}
\label{fig:377}
\end{figure}

@@

\begin{example}
\label{eg:base-1-33}
Let $(\sx',0 ,\halfcan')$ be a log spin curve of genus $1$ so that $\halfcan' = P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$. In this example, we show
$$R_{\halfcan'} \cong k[u, x_3, y_3, y_4]/(x_3 y_3- \alpha uy_4, y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$
and that $(\sx', \halfcan',\{1,2\})$ is admissible.

@@

\begin{example}
\label{eg:exception-1-5}
Let $(\sx', 0, L')$ be a log spin curve of genus 1 so that $L' = P - Q + \frac{2}{5}P_1.$ Let $u \in (P_L)_1$ be any nonzero element. We obtain $\di u|_{P_1} = 0,$ since $2P -2Q \sim 0$ and by Riemann--Roch, $\dim_k (P_L)_1 = 1.$ Let $y_3 \in (R_L)_3$ be any nonzero element. We obtain $\di y_3|_{P_1} = - P_1,$ by Riemann Roch, since if $y_3$ did not have a pole at $R$, we would obtain $y_3 \in H^0(\sx,3P-3Q) \cong H^0(\sx, P - Q) \cong 0$ as $P \neq Q$. Finally, let $y_5 \in (R_L)_5$ be an element with $y_5|_{P_1} = -P_1$. Then, we claim there is some $\alpha \in k$ so that
$R_L \cong k[u, y_3, y_5]/(y_3^4 - \alpha uy_5^2).$

@@

Note that $(\sx', \halfcan', \{1\})$ is admissible, as can be checked in a fashion analogous to the verification in Example ~\ref{eg:base-1-33}.
\end{example}
